Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-17 article.rnw
Add a reference with another example of a priori species grouping.

In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
% please add a reference to http://dx.doi.org/10.1086/713082 to the above
The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.
However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX, bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful way using less data than required for a fully pairwise parameterisation.

>>>>

In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.
However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX, bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful way using less data than required for a fully pairwise parameterisation.
